TEXT

### 2020-09-10 Article/ici_submm_cloudcorr.tex
added new plots in AWS section

%As the QRNN predictions are in form of quantiles, each prediction has an uncertainty estimate associated with it. Case specific uncertainty estimates can be quite useful but estimates of uncertainty fitted to a Gaussian model of random errors are potentially easier to implement in NWP models. To inspect if the predictions given by QRNN follow a normal distribution, we evaluated the length of confidence intervals from the median. Figure~\ref{fig:prediction_uncertainty_aws-34} shows the prediction uncertainty in AWS-34 for different quantiles. The red line represents the uncertainty in a hypothetical Gaussian distribution of $270\pm0.62$\,K. The high variability in the uncertainty estimates indicates that QRNN can successfully represent uncertainties for multiple types of cases in the individually, rather than having just a single summary measure of uncertainty about the whole scene.

%If the underlying distribution is Gaussian, the prediction uncertainties should be symmetric around the median, and equally spaced for $1\sigma$, $2\sigma$ and so on. The predictions around the median for the 94\% confidence interval ($\pm 2 \sigma$). The figure also shows that the uncertainties for all 1000 random cases are concentrated along a narrow width, thus suggesting that the case to case variability of the uncertainty is low. A similar uncertainty quantification for other 183\,GHz channels also gives similar results.

In order to analyse the performance of QRNN with task difficulty, the interrelation between the uncertainty estimates and cloud impact was investigated. Fig~\ref{fig:uncertainty_cloud_impact} displays the plot between mean uncertainty estimates for $2\sigma$ confidence interval and the cloud impact. For all five channels, the predictions with small or relatively low cloud signal have a low uncertainty or in other words have high sharpness. As fraction of cloud impact increases, the predictions are associated with high uncertainty. If we assume that higher cloud impact is representative of increase in task difficulty, the uncertainty of predictions increases with task difficulty.

%On the other hand, in order to examine if task difficulty also decreased the accuracy, we plotted the error distribution binned according to the cloud impact.

@@

>>>>

In this section, we analyse the uncertainty estimates obtained from QRNN.  Figure~\ref{fig:prediction_uncertainty_aws-34} displays the prediction uncertainty in AWS-34 for different quantiles. The prediction uncertainty has been plotted as the deviation from the median value.  The different lines represent 1500 randomly chosen cases.  The red line represents the uncertainty in a hypothetical Gaussian distribution of $270\pm0.62$\,K, which is of the order of standard deviation of predictions for AWS-34 (see Table~\ref{tab:statistics_aws}). The high variability in the uncertainty estimates indicates that QRNN can successfully represent uncertainties for each case individually, rather than expressing them as a single measure for all cases. In the latter case, the uncertainty estimates would be concentrated along a narrow interval. Also, for majority of the cases, the prediction uncertainties are symmetric around the median, specially around  the 68\% ($\pm 1 \sigma$) and 94\% confidence interval ($\pm 2 \sigma$), suggesting that the posterior distribution follows a Gaussian distribution.

In order to analyse the performance of QRNN with task difficulty, the interrelation between the uncertainty estimates and cloud impact was investigated. Here we assume that cloud impact is representative of task difficulty. Fig~\ref{fig:uncertainty_cloud_impact} displays the plot between mean uncertainty estimates for $2\sigma$ confidence interval and the cloud impact. For all five channels, the predictions with small or relatively low cloud signal have a low uncertainty or in other words have high sharpness. As fraction of cloud impact increases, the predictions become increasingly uncertain. However, this does not imply that the prediction accuracy is low. The calibration between prediction errors and measure of uncertainty should not be affected by task difficulty.

@@

%As the QRNN predictions are in form of quantiles, each prediction has an uncertainty estimate associated with it. Case specific uncertainty estimates can be quite useful but estimates of uncertainty fitted to a Gaussian model of random errors are potentially easier to implement in NWP models. To inspect if the predictions given by QRNN follow a normal distribution, we evaluated the length of confidence intervals from the median.
